When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
inserted H1b table

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels",
  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

>>>>

```{r H1b-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels",
  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```
